Dual selection games

### 2019-10-11 articles/dual-selection-games/article.tex
remove unused AMS classification
submission-ready dual game draft

\subjclass[2010]{54C30, 54D20, 54D45, 91A44}

@@

A class of such games heavily studied in the literature (see \cite{MR1378387} and its
many sequels) are selection games.

@@

Put another way, \(\mc R\) is a reflection of \(\mc A\) if for every \(A\in\mc A\),
there exists \(f\in\mathbf C(\mc R)\) such that \(\ran f\in\mc A\) and \(\ran f\subseteq A\).

@@

So a predetermined strategy ignores all moves of the opponent during the
game (all moves were decided before the game began).

\begin{definition}
  A \term{Markov strategy} for the second player \(\plII\)
  in a game \(G\) with moveset \(M\) is a function
  \(\sigma:M\times\omega\to M\). This strategy is said to be winning if
  for all possible attacks \(\alpha\in M^\omega\) by their opponent,
  the first player wins the game by playing \(\sigma(\alpha(n),n)\)
  during round \(n\).
\end{definition}

@@

\begin{definition}
  Write \(\plI\win G\) (resp. \(\plI\prewin G\)) if player \(\plI\) has a winning
  strategy (resp. winning predetermined strategy) for the game \(G\). Similarly,
  write \(\plII\win G\) (resp. \(\plII\markwin G\)) if player \(\plII\) has a winning
  strategy (resp. winning Markov strategy) for the game \(G\).
\end{definition}

Of course, \(\plII\markwin G\Rightarrow \plII\win G\Rightarrow \plI\notwin G\Rightarrow \plI\notprewin G\).
In general, none of these implications (not even the second \cite{MR0054922}) can be reversed.

It's worth noting that \(\plI\notprewin \schStrongSelGame{\mc A}{\mc B}\) is equivalent
to the selection principle often denoted \(\schStrongSelProp{\mc A}{\mc B}\) in the literature.

The goal of this paper is to characerize when two games are ``dual'' in the following
senses.

@@

@@

The following four theorems demonstrate that reflections characterize
dual selection games for both perfect information strategies and
certain limited information strategies.

The duality of the Rothberger game \(\schStrongSelGame{\mc O_X}{\mc O_X}\)
and the point-open game on \(X\) for perfect information strategies
was first noted by Galvin in \cite{MR0493925}, and
for Markov-information strategies by Clontz and Holshouser in
[TODO cite]. These proofs may be generalized as follows.

@@

\begin{corollary}
  If \(\mc R\) is a reflection of \(\mc A\),
  then \(\schStrongSelGame{\mc A}{\mc B}\) and \(\schStrongSelGame{\mc R}{\neg\mc B}\)
  are both perfect information dual and Markov information dual.
\end{corollary}

@@

While these notions were defined in terms of a particular basis, the reader may verify the the following.

\begin{proposition}
  Let \(\mc A'\) be a selection basis for \(\mc A\).
  \begin{itemize}
    \item \(\plI\win\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plI\win\schStrongSelGame{\mc A'}{\mc B}\).
    \item \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plI\prewin\schStrongSelGame{\mc A'}{\mc B}\).
    \item \(\plII\win\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plII\win\schStrongSelGame{\mc A'}{\mc B}\).
    \item \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plII\markwin\schStrongSelGame{\mc A'}{\mc B}\).
  \end{itemize}
\end{proposition}

\begin{proposition}
  Each selection set in Definition \ref{selectionSets} is a selection basis for the set
  defined by replacing \(\mc T_X\) with the set of all nonempty open sets in \(X\).
\end{proposition}

As such, the choice of topological basis is irrelevant when playing selection games using these sets.

We may now establish (or re-establish) the following dual games.

\begin{proposition}
  \(\mc P_X\) is a reflection of \(\mc O_X\).
\end{proposition}
\begin{proof}
  For every open cover \(\mc U\), the corresponding choice function \(f\in\mathbf C(\mc P_X)\) is simply
  the witness that \(x\in f(\mc T_{X,x})\in\mc U\).
\end{proof}

\begin{corollary}
  \(\schStrongSelGame{\mc O_X}{\mc B}\) and \(\schStrongSelGame{\mc P_X}{\neg\mc B}\) are perfect-information
  and Markov-information dual.
\end{corollary}

In the case that \(\mc B=\mc O_X\), \(\schStrongSelGame{\mc O_X}{\mc O_X}\) is the well-known Rothberger game,
and \(\schStrongSelGame{\mc P_X}{\neg\mc O_X}\) is isomorphic
to the point-open game \(PO(X)\): \(\plI\) chooses points of \(X\), \(\plII\) chooses an open neighborhood
of each chosen point, and \(\plI\) wins if \(\plII\)'s choices are a cover.
So this was simply the classic result that the Rothberger game and
point-open game are perfect-information dual \cite{MR0493925}, and the more recent result that
these games are Markov-information dual [TODO cite clontzHols].

\begin{proposition}
  \(\mc F_X\) is a reflection of \(\Omega_X\).
\end{proposition}
\begin{proof}
  For every \(\omega\)-cover \(\mc U\), the corresponding choice function \(f\in\mathbf C(\mc F_X)\) is simply
  the witness that \(F\subseteq f(\mc T_{X,F})\in\mc U\).
\end{proof}

\begin{corollary}
  \(\schStrongSelGame{\Omega_X}{\mc B}\) and \(\schStrongSelGame{\mc F_X}{\neg\mc B}\) are perfect-information
  and Markov-information dual.
\end{corollary}

Note that in the case that \(\mc B=\Omega_X\), \(\schStrongSelGame{\Omega_X}{\Omega_X}\) is the Rothberger
game played with \(\omega\)-covers, and \(\schStrongSelGame{\mc F_X}{\neg\Omega_X}\) is isomorphic
to the \(\Omega\)-finite-open game \(\Omega FO(X)\): \(\plI\) chooses finite subsets of \(X\), \(\plII\) chooses an open neighborhood
of each chosen finite set, and \(\plI\) wins if \(\plII\)'s choices are an \(\omega\)-cover.
These games were shown to be dual in [TODO cite clontzHols].

\begin{proposition}
  \(\mc T_X\) is a reflection of \(\mc D_X\).
\end{proposition}
\begin{proof}
  For every dense \(D\), the corresponding choice function \(f\in\mathbf C(\mc T_X)\) is simply
  the witness that \(f(U)\in U\cap D\).
\end{proof}

@@

In the case that \(\mc B=\Omega_{X,x}\) for some \(x\in X\), \(\schStrongSelGame{\mc D_X}{\Omega_{X,x}}\) is
the strong countable dense fan-tightness game at \(x\), see e.g. \cite{MR2678950}. \(\schStrongSelGame{\mc T_X}{\neg\Omega_{X,x}}\)
is the game \(CL(X,x)\) first studied by Tkachuk in \cite{tkachukTwoPointGame}. Tkachuk showed in that paper
that these games are perfect-information dual; Clontz and Holshouser previously showed these were Markov-information
dual in the case that \(X=C_p(Y)\) [TODO cite].

In the case that \(\mc B=D_X\), then \(\schStrongSelGame{\mc D_X}{\mc D_X}\) is the strong selective
separability game introduced in \cite{MR1711901}, and \(\schStrongSelGame{\mc T_X}{\neg\mc D_X}\) is the
point-picking game of Berner and Juh\'asz defined in \cite{MR775687}. Scheepers showed that these
were perfect-information dual in his paper.

\begin{proposition}
  \(\mc T_{X,x}\) is a reflection of \(\Omega_{X,x}\).
\end{proposition}
\begin{proof}
  For every set \(Y\) with limit point \(x\), the corresponding choice function \(f\in\mathbf C(\mc T_{X,x})\) is simply
  the witness that \(f(U)\in U\cap Y\).
\end{proof}

\begin{corollary}
  \(\schStrongSelGame{\Omega_{X,x}}{\mc B}\) and \(\schStrongSelGame{\mc T_{X,x}}{\neg\mc B}\) are perfect-information
  and Markov-information dual.
\end{corollary}

@@

\begin{corollary}
  \(\plI\notprewin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\)
  if and only if
  \(\plI\notwin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\).
\end{corollary} 
\begin{proof}
  As shown in \cite{MR510910},
  a space is \(w\) at \(x\), that is, \(\plII\notwin\schStrongSelGame{\mc T_{X,x}}{\neg\Gamma_{X,x}}\) 
  if and only if \(\plI\notprewin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\) for all \(x\in X\).
\end{proof}

@@

%Finally, consider the following result from \cite{2016arXiv161004800C}.
%
%\begin{proposition}
%  
%\end{proposition}

@@

\begin{question}
  Does there exist a natural reflection for \(\Gamma_{X,x}\)
  or \(\Gamma_X=\{\mc U\subseteq\mc T_X:\forall x\in X(\mc U\setminus\mc T_{X,x}\in[T_X]^{<\aleph_0})\}\)?
\end{question}

\begin{question}
  Can these results be extended for \(\schSelGame{\mc A}{\mc B}\)?
\end{question}

>>>>

\subjclass[2010]{54D20, 54D45, 91A44}

@@

A class of such games heavily studied in the literature, particularly
topology (see \cite{MR1378387} and its
many sequels), are selection games.

@@

Put another way, \(\mc R\) is a reflection of \(\mc A\) if \(\ran f\in\mc A\) 
for all \(f\in\mathbf C(\mc R)\), and for each \(A\in\mc A\) there exists
\(f_A\in\mathbf C(\mc R)\) such that \(\ran{f_A}\subseteq A\).

@@

So a predetermined strategy ignores all moves of the opponent during the
game (all moves were decided before the game began). Such strategies
are also known as \(0\)-Markov strategies or \(0\)-Markov tactics.
The following definition is similarly also known as a \(1\)-Markov strategy.

\begin{definition}
  A \term{Markov strategy} for the second player \(\plII\)
  in a game \(G\) with moveset \(M\) is a function
  \(\sigma:M\times\omega\to M\). This strategy is said to be winning if
  for all possible attacks \(\alpha\in M^\omega\) by their opponent,
  the second player wins the game by playing \(\sigma(\alpha(n),n)\)
  during round \(n\).
\end{definition}

@@

We also consider similar strategies that ignore the round number.

\begin{definition}
  A \term{constant strategy} for the first player \(\plI\)
  in a game \(G\) with moveset \(M\) is simply a choice \(m\in M\).
  This strategy is said to be winning if
  for all possible attacks \(\alpha\in M^\omega\) by their opponent,
  the first player wins the game by playing \(m\) during every round.
\end{definition}

\begin{definition}
  A \term{tactical strategy} for the second player \(\plII\)
  in a game \(G\) with moveset \(M\) is a function
  \(\sigma:M\to M\). This strategy is said to be winning if
  for all possible attacks \(\alpha\in M^\omega\) by their opponent,
  the second player wins the game by playing \(\sigma(\alpha(n))\)
  during round \(n\).
\end{definition}

\begin{definition}
  Write \(\plI\win G\) (resp. \(\plI\prewin G\), \(\plI\conwin G\)) 
  if player \(\plI\) has a winning
  strategy (resp. winning predetermined/constant strategy) for the game \(G\). Similarly,
  write \(\plII\win G\) (resp. \(\plII\markwin G\), \(\plII\tactwin G\)) 
  if player \(\plII\) has a winning
  strategy (resp. winning Markov/tactical strategy) for the game \(G\).
\end{definition}

Of course: 
\[
  \plII\tactwin G\Rightarrow 
  \plII\markwin G\Rightarrow 
  \plII\win G\Rightarrow 
  \plI\notwin G\Rightarrow 
  \plI\notprewin G\Rightarrow 
  \plI\notconwin G
.\]
In general, none of these implications (not even the middle \cite{MR0054922}) can be reversed.

While predetermined and constant strategies are rarely explicitly studied in the literature,
they are implicitly considered when studying the following well-known principles.

\begin{definition}
  The selection principle \(\schStrongSelProp{\mc A}{\mc B}\) asserts
  that for each sequence \(\setB{A_n}{n<\omega}\in[\mc A]^\omega\),
  there exist \(B_n\in A_n\) such that \(\setB{B_n}{n<\omega}\in\mc B\).
\end{definition}

For example, if \(\mc O_X\) denotes the open covers of a space \(X\), 
then \(\schStrongSelProp{\mc O_X}{\mc O_X}\) is the Rothberger covering property.

\begin{definition}
  The choice principle \(\binom{\mc A}{\mc B}^\kappa\) asserts
  that for each \(A\in \mc A\), there exists a subset
  \(B\subseteq A\) where \(|B|=\kappa\) and \(B\in\mc B\).
\end{definition}

For example,
\(\binom{\mc O_X}{\mc O_X}^\omega\) is the Lindel\"of covering property.

\begin{proposition}
  \(\schStrongSelProp{\mc A}{\mc B}\) is equivalent to
  \(\plI\notprewin \schStrongSelGame{\mc A}{\mc B}\), and
  \(\binom{\mc A}{\mc B}^\omega\) is equivalent to
  \(\plI\notconwin \schStrongSelGame{\mc A}{\mc B}\).
\end{proposition}

\begin{proof}
  The first equivalence is direct from their defintions.

  To see the second,
  assume \(\binom{\mc A}{\mc B}^\omega\). Then given a constant strategy
  \(A\in\mc A\) for \(\plI\), \(\plII\) uses \(\binom{\mc A}{\mc B}^\omega\) to
  choose \(B=\setB{b_n}{n<\omega}\subseteq A\) where \(B\in\mc B\); thus
  playing \(b_n\) in round
  \(n\) defeats \(\plI\)'s constant strategy.

  Likewise, assuming 
  \(\plI\notconwin \schStrongSelGame{\mc A}{\mc B}\), for each constant strategy
  \(A\in\mc A\) for \(\plI\) there must be a counterattack playing \(b_n\in A\)
  during each round \(n\) such that \(\setB{b_n}{n<\omega}\in\mc B\); this witnesses
  \(\binom{\mc A}{\mc B}^\omega\).
\end{proof}

The goal of this paper is to characterize when two games are ``dual'' in the following
senses.

\begin{definition}
  A pair of games \(G(X),H(X)\) defined for a topological space \(X\)
  are \term{tactical information dual} if both
  of the following hold.
  \begin{itemize}
    \item \(I\conwin G(X)\) if and only if \(II\tactwin H(X)\).
    \item \(II\tactwin G(X)\) if and only if \(I\conwin H(X)\).
  \end{itemize}
\end{definition}

@@

\begin{definition}
  A pair of games \(G(X),H(X)\) defined for a topological space \(X\)
  are \term{dual} if they are tactial, Markov, and perfect information
  dual.
\end{definition}

@@

The following six theorems demonstrate that reflections characterize
dual selection games for perfect information strategies and
certain limited information strategies.

For example,
the duality of the Rothberger game \(\schStrongSelGame{\mc O_X}{\mc O_X}\)
and the point-open game on \(X\) for perfect information strategies
was first noted by Galvin in \cite{MR0493925}, and
for Markov-information strategies by Clontz and Holshouser in
\cite{CLONTZ2019106815}. These proofs may be generalized as follows.

  Then
  \(\plI\conwin\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plII\tactwin\schStrongSelGame{\mc R}{\neg\mc B}\).
\end{theorem}

\begin{proof}
  Let \(A\) witness 
  \(\plI\conwin\schStrongSelGame{\mc A}{\mc B}\).
  Since \(A\in\mc A\),
  \(\ran{\tau}\subseteq A\)
  for some \(\tau\in\mathbf C(\mc R)\). 
  Suppose \(R_n\in \mc R\) for all \(n<\omega\).
  Note that since \(A\) is winning and 
  \(\tau(R_n)\in\ran{\tau}\subseteq A\),
  \(\{\tau(R_n):n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plII\tactwin\schStrongSelGame{\mc R}{\neg\mc B}\).

  Now let \(\sigma\) witness
  \(\plII\tactwin\schStrongSelGame{\mc R}{\neg\mc B}\).
  Then \(\sigma\in\mathbf C(\mc R)\) and we may let
  \(A=\ran{\sigma}\in\mc A\). 
  Suppose that \(B_n\in A=\ran{\sigma}\) for
  all \(n<\omega\). Choose \(R_n\in\mc R\) such that 
  \(B_n=\sigma(R_n)\). Since \(\sigma\) is winning,
  \(\{B_n:n<\omega\}\not\in\mc B\). Thus \(A\) witnesses
  \(\plI\conwin\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

  Then
  \(\plII\tactwin\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plI\conwin\schStrongSelGame{\mc R}{\neg\mc B}\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) witness 
  \(\plII\tactwin\schStrongSelGame{\mc A}{\mc B}\).
  Suppose that for each \(R\in\mc R\),
  there was \(g(R)\in R\) such that for all \(A\in \mc A\),
  \(\sigma(A)\not=g(R)\). Then \(g\in\mathbf C(\mc R)\)
  and \(\ran g\in\mc A\),
  thus \(\sigma(\ran g)\not=g(R)\) for all \(R\in\mc R\),
  a contradiction.

  So choose \(R\in\mc R\) such that for all \(r\in R\)
  there exists \(A_r\in\mc A\) such that \(\sigma(A_r)=r\).
  It follows that when \(r_n\in R\) for \(n<\omega\),
  \(\{r_n:n<\omega\}=\{\sigma(A_{r_n}):n<\omega\}\in B\),
  so \(R\) witnesses
  \(\plI\conwin\schStrongSelGame{\mc R}{\neg\mc B}\).

  Now let \(R\) witness 
  \(\plI\conwin\schStrongSelGame{\mc R}{\neg\mc B}\).
  Then \(R\in\mc R\), so for \(A\in\mc A\), let
  \(f_A\in\mathbf C(\mc R)\) satisfy \(\ran{f_A}\subseteq A\),
  and let \(\tau(A)=f_A(R)\in A\cap R\).
  Then if \(A_n\in\mc A\) for \(n<\omega\), \(\tau(A_n)\in R\),
  so \(\{\tau(A_n):n<\omega\}\in\mc B\).
  Thus \(\tau\) witnesses
  \(\plII\tactwin\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

@@

\begin{corollary}\label{mainResult}
  If \(\mc R\) is a reflection of \(\mc A\),
  then \(\schStrongSelGame{\mc A}{\mc B}\) and \(\schStrongSelGame{\mc R}{\neg\mc B}\)
  are  dual.
\end{corollary}

@@

%While these notions were defined in terms of a particular basis, the reader may verify the the following.
%
%\begin{proposition}
%  Let \(\mc A'\) be a selection basis for \(\mc A\).
%  \begin{itemize}
%    \item \(\plI\win\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plI\win\schStrongSelGame{\mc A'}{\mc B}\).
%    \item \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plI\prewin\schStrongSelGame{\mc A'}{\mc B}\).
%    \item \(\plII\win\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plII\win\schStrongSelGame{\mc A'}{\mc B}\).
%    \item \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plII\markwin\schStrongSelGame{\mc A'}{\mc B}\).
%  \end{itemize}
%\end{proposition}
%
%\begin{proposition}
%  Each selection set in Definition \ref{selectionSets} is a selection basis for the set
%  defined by replacing \(\mc T_X\) with the set of all nonempty open sets in \(X\).
%\end{proposition}
%
%As such, the choice of topological basis is irrelevant when playing selection games using these sets.

We may now establish the following dual games.

\begin{proposition}
  \(\mc P_X\) is a reflection of \(\mc O_X\).
\end{proposition}
\begin{proof}
  For every basic open cover \(\mc U\), the corresponding choice function \(f_{\mc U}\in\mathbf C(\mc P_X)\) is simply
  the witness that for each \(\mc T_{X,x}\in\mc P_X\), there exists \(f_{\mc U}(\mc T_{X,x})\in\mc U\) such that
  \(x\in f_{\mc U}(\mc T_{X,x})\).
\end{proof}

\begin{corollary}\label{coverSel1}
  \(\schStrongSelGame{\mc O_X}{\mc B}\) and \(\schStrongSelGame{\mc P_X}{\neg\mc B}\) are dual.
\end{corollary}

In the case that \(\mc B=\mc O_X\), \(\schStrongSelGame{\mc O_X}{\mc O_X}\) is the well-known Rothberger game,
and \(\schStrongSelGame{\mc P_X}{\neg\mc O_X}\) is isomorphic
to the point-open game \(PO(X)\): \(\plI\) chooses points of \(X\), \(\plII\) chooses an open neighborhood
of each chosen point, and \(\plI\) wins if \(\plII\)'s choices are a cover.
So this encapsulates the classic result that the Rothberger game and
point-open game are perfect-information dual \cite{MR0493925}, the more recent result that
these games are Markov-information dual \cite{CLONTZ2019106815}, and the quickly verified fact that
a Lindel\"of space \(X\) may be characterized as follows: for each neighborhood assignment (i.e.
tactic for \(\plII\) in \(PO(X)\)) there exists a countable subset
of \(X\) such that its neighborhoods cover the space.

\begin{proposition}
  \(\mc F_X\) is a reflection of \(\Omega_X\).
\end{proposition}
\begin{proof}
  For every basic open \(\omega\)-cover \(\mc U\), the corresponding choice function \(f_{\mc U}\in\mathbf C(\mc F_X)\) is simply
  the witness that for each \(\mc T_{X,F}\in\mc F_X\), there exists \(f_{\mc U}(\mc T_{X,F})\in\mc U\) such that
  \(F\subseteq f_{\mc U}(\mc T_{X,F})\).
\end{proof}

\begin{corollary}\label{coverSel2}
  \(\schStrongSelGame{\Omega_X}{\mc B}\) and \(\schStrongSelGame{\mc F_X}{\neg\mc B}\) are dual.
\end{corollary}

Note that in the case that \(\mc B=\Omega_X\), \(\schStrongSelGame{\Omega_X}{\Omega_X}\) is the Rothberger
game played with \(\omega\)-covers, and \(\schStrongSelGame{\mc F_X}{\neg\Omega_X}\) is isomorphic
to the \(\Omega\)-finite-open game \(\Omega FO(X)\): \(\plI\) chooses finite subsets of \(X\), \(\plII\) chooses an open neighborhood
of each chosen finite set, and \(\plI\) wins if \(\plII\)'s choices are an \(\omega\)-cover.
These games were directly shown to be Markov and perfect-information dual in \cite{CLONTZ2019106815}.

\begin{proposition}
  \(\mc T_X\) is a reflection of \(\mc D_X\).
\end{proposition}
\begin{proof}
  For every dense \(D\), the corresponding choice function \(f_D\in\mathbf C(\mc T_X)\) is simply
  the witness that for each \(U\in\mc T_X\), there exists \(f_D(U)\in U\cap D\).
\end{proof}

@@

In the case that \(\mc B=\Omega_{X,x}\) for some \(x\in X\), \(\schStrongSelGame{\mc D_X}{\Omega_{X,x}}\) is
the strong countable dense fan-tightness game at \(x\), see e.g. \cite{MR2678950}. \(\schStrongSelGame{\mc T_X}{\neg\Omega_{X,x}}\)
is the game \(CL(X,x)\) first studied by Tkachuk in \cite{tkachukTwoPointGame}. Tkachuk showed in that paper
that these games are perfect-information dual; Clontz and Holshouser previously showed these were Markov-information
dual in the case that \(X=C_p(Y)\)  \cite{CLONTZ2019106815}.

In the case that \(\mc B=D_X\), then \(\schStrongSelGame{\mc D_X}{\mc D_X}\) is the strong selective
separability game introduced by Scheepers 
in \cite{MR1711901}, and \(\schStrongSelGame{\mc T_X}{\neg\mc D_X}\) is the
point-picking game of Berner and Juh\'asz defined in \cite{MR775687}. Scheepers showed that these
were perfect-information dual in his paper.

\begin{proposition}
  \(\mc T_{X,x}\) is a reflection of \(\Omega_{X,x}\).
\end{proposition}
\begin{proof}
  For every set \(Y\) with limit point \(x\), the corresponding choice function \(f_Y\in\mathbf C(\mc T_{X,x})\) is simply
  the witness that for each \(U\in\mc T_{X,x}\), there exists \(f_Y(U)\in U\cap Y\).
\end{proof}

\begin{corollary}
  \(\schStrongSelGame{\Omega_{X,x}}{\mc B}\) and \(\schStrongSelGame{\mc T_{X,x}}{\neg\mc B}\) are dual.
\end{corollary}

@@

\begin{corollary}
  \(\plI\notprewin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\)
  if and only if
  \(\plI\notwin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\).
\end{corollary} 
\begin{proof}
  As shown in \cite{MR510910},
  \(\plII\notwin\schStrongSelGame{\mc T_{X,x}}{\neg\Gamma_{X,x}}\) (i.e. \(X\) is \(w\) in the
  terminology of that paper)
  if and only if \(\plI\notprewin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\).
  The result follows as 
  \(\schStrongSelGame{\mc T_{X,x}}{\neg\Gamma_{X,x}}\) and
  \(\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\) are dual.
\end{proof}

@@

We conclude by noting how Corollary \ref{mainResult}
was used by the authors of \cite{MR3991109} to
easily strengthen Propositions \ref{coverSel1} and \ref{coverSel2}
while this paper was still in preparation.

\begin{definition}
Let \(\mc Q\) be a collection of subsets of a topological space \(X\).
Then \(\mc O_{X,\mc Q}\) is the collection of basic open covers \(\mc U\) such that for
each \(Q\in\mc Q\), there is \(U\in\mc U\) with \(Q\subseteq U\).
Likewise, \(\mc N_{X,\mc Q}=\{\mc T_{X,Q}:Q\in\mc Q\}\) where each \(\mc T_{X,Q}\) collects all
basic open sets \(U\) such that \(Q\subseteq U\). 
\end{definition}

In particular, \(\mc O_{X,[X]^1}=\mc O_X\) and \(\mc O_{X,[X]^{<\omega}}=\Omega_X\).
Likewise \(\mc N_{X,[X]^1}=\mc P_X\) and \(\mc N_{X,[X]^{<\omega}}=\mc F_X\).

\begin{theorem}[\cite{MR3991109}]
  The games \(\schStrongSelGame{\mc O_{X,\mc Q}}{\mc B}\) and
  \(\schStrongSelGame{\mc N_{X,\mc Q}}{\neg\mc B}\) are dual.
\end{theorem}

\begin{proof}
  This is immediate as \(\mc N_{X,\mc Q}\) reflects \(\mc O_{X,\mc Q}\). 
  To see this, for each
  \(\mc U\in\mc O_{X,\mc Q}\), choose \(f_{\mc U}\in\mathbf C(\mc N_{X,\mc Q})\)
  satisfying that for each \(\mc T_{X,Q}\in\mc N_{X,\mc Q}\), there exists
  \(f_{\mc U}(\mc T_{X,Q})\in\mc U\) such that \(Q\subseteq f_{\mc U}(\mc T_{X,Q})\).
\end{proof}

@@

Let 
\(\Gamma_X=\{\mc U\subseteq\mc T_X:\forall x\in X(\mc U\setminus\mc T_{X,x}\in[T_X]^{<\aleph_0})\}\). 
Such \(\gamma\)-covers are related to the convergent sequences of \(C_p(X)\) (that is,
\(\Gamma_{C_p(X),\mathbf 0}\) as defined in Definition \ref{selectionSets}),
see e.g. \cite{BUKOVSKY2019239}.

\begin{question}
  Does there exist a natural reflection for \(\Gamma_{X,x}\)
  or \(\Gamma_X\)?
\end{question}

The game \(\schSelGame{\mc A}{\mc B}\) is defined analogously to
\(\schStrongSelGame{\mc A}{\mc B}\), except \(\plII\) may choose a finite subset each round
rather than a single set.

\begin{question}
  Do there exist any duality results for \(\schSelGame{\mc A}{\mc B}\) similar to the technique
  of reflections?
\end{question}
